---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scanr.data
 
<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of scanr.data is to bring utility functions for dealing with scanr data, within R. 

Features includes all the necessary function to begin data-science within R, from the scanr data : 

From a folder with several .jsonl or .jsonl.gz files : 

1. *convert each .jsonl or .jsonl.gz files to a .parquet database file*
2. *unnest the 'denormalized' .json structure, i.e. adding nested data.frame and list as columns of the main data.frame* 
3. *deal with all the merging*

[TODO]

## Installation

You can install the development version of scanr.data from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Clement-LVD/scanr.data")
```

## Examples

TODO

```{r example}
# library(scanr.data)
## basic example code
```
 